\LARGE \bf Efficient Sampling for Grasp Quality Evaluation on Gaussian Process Implicit Surface Representations [v-12 09-30-2014]

### 2014-10-01 paper-pieter-feedback.tex
gitignore, changed citation style

\begin{abstract}
Gaussian Process Implicit Surface (GPIS) have emerged recently as a new Bayesian shape representation.  Former methods for grasp evaluation with shape uncertainty require sampling from  distributions on shape. The standard approach of drawing samples from a GPIS in 2D by means of a evaluation on a uniform grid has a complexity of $O(n^6)$(2D) and $O(n^9)$ in the number of grid steps $n$.. We propose an alternative approximation to sampling from shape distributions and demonstrate how that reduce complexity from $O(n^6)$ in 2D and $O(n^9)$ in 3D to $O(n^3)$ for evaluation of a single grasp. We furthermore introduce the idea of adaptive sampling in this context by formulating it as a multi-arm bandit problem for speeding up the selection of the highest quality grasp in a set of proposed grasps. 
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

@@

\todo{Get High res GPIS visualizations, Incorporate next round of feedback}
Consider a robot packing boxes in a shipping warehouse environment. The robot will frequently encounter objects that it has not seen before. The robot will have to plan stable grasps without any prior information other than its sensor data. As seen in Fig. \ref{fig:noisy data}, with today's RGB and depth sensors, surface properties, such as specularity and transparency, can greatly effect the returned observations. Grasp planners based on deterministic algorithms are not designed to handle such noise and could fail. To plan grasps in a partially observed world, recent research has focused on incorporating uncertainity in the shape of the object \cite{kehoe2012estimating} \cite{kehoe2012estimating} \cite{christopoulos2007handling} \cite{zheng2005}..

While past work has encoded uncertainty in a polygonal mesh representation \cite{kehoe2012estimating}, an alternative is to work with the signed distance fields (SDFs), a continuous valued function that is an implicit surface: zero-valued at the surface of the object, positive value outside the surface and negative valued inside the surface. This representation is growing in popularity in the robotics field for its ability to integrate range data in real time \cite{newcombe2011kinectfusion}\cite{curless1996volumetric}. To incorporate uncertainty one can use a Gaussian Process Implicit Surface (GPIS), a Gaussian process over signed distance field. Not only does GPIS present a straightforward and formal way to incorporate measurements from visual, laser and tactile sensors, they  also allow for a continuous differentiable function on shape, which can be used for a feedback grasp controller, finding locally optimal grasps and active exploration  \cite{dragiev2011}\cite{jeffs}\cite{hollinger2013}.

\begin{figure}[ht!]
\centering
\includegraphics[width=8.5cm,height=4cm]{figures/Slide02.jpg}
\caption{\footnotesize
Left: HD image of a common measuring cup from in a household environment. Right: Image taken from PR2's Primesense Carmine sensor, large parts of the measuring cup are not detected by the depth sensor and are not visible in the RGB image.}
\vspace*{-10pt}
\label{fig:noisy data}
\end{figure}

Given a method to represent shape uncertainty, a common technique to evaluate grasp quality is to sample from the distribution on shape and perform Monte-Carlo integration on a given grasp metric \cite{kehoe2012estimating}\cite{kehoe2012toward}\cite{christopoulos2007handling}. Applying this technique to GPIS requires an exhaustive sampling of the signed distance field, which scales $O(n^6)$ for a 2D $n \times n$ workspace and $O(n^9)$ for a 3D workspace.The computationally complexity of sampling is derived from the fact sampling from a Gaussian requires matrix inversion of the entire signed distance field. Our paper reduces this complexity to $O(n^3)$ by using the insight that for grasp quality evaluation one only cares about the parameters that define a grasp: contacts points, surface normals, center of mass and friction coefficient \cite{pokorny2013classical}. We constrain the contact points by considering the approach trajectory of a gripper.  Hence, sampling the whole signed distance field is not needed, but instead one can only work with the distributions on grasp parameters given the shape uncertainty model and gripper trajectory. In light of this our contributions are the following:

\begin{enumerate}
	\item Derivation of  distributions on grasp parameters given GPIS shape uncertainty model and approach trajectory of gripper.
	\item  Demonstrating both theoretically and empirically how those distributions reduce the computationally complexity of sampling.
	\item Applying adaptive sampling techniques to efficiently find high quality grasps in a given set of proposed grasps. 
\end{enumerate}

@@

 Past work on grasping under uncertainty has focused on state uncertainty \cite{goldberg1990bayesian}\cite{goldberg1990stochastic} \cite{stulp2011learning},  uncertainty in object pose \cite{christopoulos2007handling}  \cite{felip2009robust} \cite{kim2012physically} or uncertainty in the location of contact with the object \cite{zheng2005}. Robust grasp selection for parallel jaw grippers on uncertain shapes was studied by Kehoe et al. for both zero-slip push grasps \cite{kehoe2012toward} and slip push grasps \cite{kehoe2012estimating} using Monte Carlo integration for the expected grasp quality, but this approach was limited to polygonal shapes.  Christopoulo et al. sampled spline fits for 2-dimensional planar objects to measure the quality of uncertainty, however it is has not been shown how a spline based method could incorporate non-visual sensing information for representing shape uncertainty.

 The choice of using Gaussian Process Implicit Surfaces to represent uncertainty, is based on the fact it provides a formal way to include various sources of noise from observations such as tactile, laser and visual. Futhermore, implicit surface representations are becoming increasingly popular in robotics due to their success in real-time surface modeling from range images \cite{curless1996volumetric}\cite{newcombe2011kinectfusion}\cite{hornung2013octomap}. Some exciting work done with GPIS representation are the following: Hollinger et al. used GPIS to perform active sensing on the hulls in underwater boats \cite{hollinger2013}. Dragiev et al. showed how GPIS can represent shapes for grasps and used  as a grasp controller on the continuous signed distance function \cite{dragiev2011}. Mahler et al. used GPIS representation to find locally optimal grasps by framing grasp planning as an optimization problem \cite{jeff}.

  For grasp quality evaluation with shape uncertainty a common method involves sampling from the distribution on shape \cite{kehoe2012estimating} \cite{kehoe2012toward} \cite{christopoulos2007handling}. With GPIS this requires computationally intensive sampling from a signed distance field that is the dimension of the workspace. We propose an alternative distribution to sample from, based on the idea that we only need to consider the approach trajectory of the gripper.

Monte-Carlo integration involves drawing random samples from a distribution to approximate an integral \cite{caflisch1998monte}. While previous work has looked at quality evaluation of a single grasp with uncertainty \cite{christopoulos2007handling}\cite{zheng2005}, few have compared many different grasps with uncertainty and efficiently chosen the best one.  Adaptive Sampling is the idea of allocating samples based on previous observations or rewards, which can be described as a multi-arm bandit problem \cite{barto1998reinforcement}. Prior work by Kehoe et al. \cite{kehoe2012toward} used an adaptive sampling approach that removed low quality grasps based on values received, but this method had no statistical guarantees and could lead to high quality grasps being removed. To achieve guarantees, we frame the problem as a "budgeted multi-arm bandit" problem, where exploration and exploitation are decoupled and the agent has to allocate resources to explore for a finite time then decide which arm to exploit  \cite{madani2004budgeted}. Drawing from the literature on Monte-Carlo sampling we estimate the confidence bounds of grasps and prune only those that are statistically distinguishable \cite{caflisch1998monte}.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width = 8.5cm, height = 14cm ]{figures/Slide03.jpg}
\caption{\footnotesize Six example objects illustrating transparency, specularity, sensor noise that illustrate the need for shape uncertainty: (from top to bottom) tape, squirt bottle, stapler, loofa, marker, water bottle. Displayed from right to left are the HD color image, a point cloud observation from a Primesense Carmine, GPIS visualization technique from \cite{jeffs}, the nominal shape on a $25 \times 25$ grid.  }
\vspace*{-10pt}
\label{fig:GPIS_TSDF}
\end{figure}
%\section{Related Work}

For our kernel choice we decided to use the square exponential kernel, a major reason for this was its differentiability. Other kernels relevant to GPIS are the thin-plate splines kernel and the Matern kernel \cite{williams2007}.

@@

The $L^1$ version of the metric works by taking as input the contact points $\textbf{c}_1,...,\textbf{c}_m$, surface normals $\textbf{n}_1,...,\textbf{n}_m$, center of mass $z$ and friction coefficient $\mu$. Then constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space. A wrench is defined as concatenation of a force and torque vector.  If the convex hull doesn't enclose the origin, the grasp is not in force-closure. Thus a grasp can be parameterized by the following tuple $g = \lbrace \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} \rbrace$, our method is applicable to all grasp metrics that represent a grasp as the tuple $g$, such as \cite{christopoulos2007handling}\cite{li1988task}.

@@

\begin{align*}
E(Q(\Gamma)) \approx \sum_{i=1}^N Q(g|S_i,\Gamma) , S_i \in p(S)
\end{align*}

@@

Thus if the workspace is an $n \times n$ grid, the joint distribution is an  $n^2$ multi-variate Gaussian, due to $sd:\mathbb{R}^2 \rightarrow \mathbb{R}$.  Sampling from a Gaussian involves inverting the covariance matrix and inversion is in the naive way $O(n^3)$ \cite{petersen2008matrix}. Thus the complexity of this operation is $O(n^6)$ in 2D and $O(n^9)$ in 3D.

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width = 17cm, height = 4.5cm]{figures/Slide04.jpg}
\caption{ \footnotesize (Left to Right): Line of action for a given gripper on an uncertain surface representing a measuring cup. Distribution $p(c)$ as a function of $t$, the position along the line of action $\gamma(t)$. The two modes correspond to the different potential contact points, either the handle or the base of the cup. Lastly, the distribution on the surface normals (inward pointing) along $\gamma(t)$ described by equation \ref{eq:normal_dist}. }
\vspace*{-10pt}
\label{fig:GraspDist}
\end{figure*}

@@

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale = 0.3]{figures/Slide06.jpg}
\caption{ \footnotesize Left: A surface with GPIS construction and expected center of mass (black X)
Right: The distribution on the density of each point assuming uniform density}
\vspace*{-10pt}
\label{fig:GPIS_MASS}
\end{figure}

@@

\section{Adaptive Sampling for Grasp Selection}
After determining how to efficiently compute the $E(Q(\Gamma))$, we need to now compute the full problem of Eq. \ref{eq:problem_def}, hence the selecting the best grasp plan $\Gamma^*$. While a standard approach to solving this problem would be to simply perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-arm bandit problem and forming a policy for selecting which grasp to sample. The motivation behind this is due to the expensive evaluation that our grasp metric Q can take \cite{ferrari1992} and the fact that the convergence of the expected quality of a typical grasp can take hundreds of evaluations as shown in Fig. \ref{fig:sampling_convergence}.

\begin{figure}[ht!]
\centering
\includegraphics[width=8.5cm,height=9cm]{figures/Slide11.jpg}
\caption{ \footnotesize Convergence of expected grasp quality, $E(Q(g))$,  for a typical grasp. You can see it can take hundreds of evaluations to correctly estimate the expected grasp quality, thus it is important to  intelligently allocate sampling resources}
\vspace*{-10pt}
\label{fig:sampling_convergence}
\end{figure}

@@

More formally an agent is given a set prior distributions $\mathcal{P}(1,...,K)$ for the K arms based on the awards seen. At each interval an arm $I_t$ is pulled based on some allocation strategy $\psi_t \in \lbrace 1,...,K \rbrace$. This happens until a stopping signal is given at which point an arm (or grasp plan) is chosen based on a recommendation strategy $\zeta_t \in \lbrace 1,...,K \rbrace$.

@@

@@

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=8.5cm,height=9cm]{figures/Slide12.jpg}
\caption{ \footnotesize Time it took to sample from 100 grasp distributions for a given resulution of the workspace. Blue line is sampling from $p(sd(\mathcal{R}))$ or shapes and Green is sampling from $p(g)$ or the calculated distribution on grasps. As you can see sampling from the calculated distributions scales much better. }
\vspace*{-10pt}
\label{fig:speed_dif}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=8.5cm,height=9cm]{figures/Slide09.jpg}
\caption{ \footnotesize Comparison of two sampling methods. Green is the adaptive bandit method that actively chooses which one to sample and Blue is the naive Monte-Carlo method. We measure their ability to converge in terms of simple regret Eq. \ref{eq:simple_regret} averaged over 100 runs. We had them determine the best grasp when $|G|=1000$. As you can see our method converges much faster with an average of evaluation of 4 samples per grasp. We start the process though by deterministically evaluating every grasp 2 times to achieve a baseline, which explains the first part of the graph.}
\vspace*{-10pt}
\label{fig:simple_regret}
\end{figure}

>>>>

\begin{abstract}
Gaussian Process Implicit Surface (GPIS) have emerged recently as a new Bayesian shape representation.  %%PA: not sure what "Bayesian shape represenation" means -- isn't it just a distribution over shapes that it represents, which happens to allow for performing Bayesian inference?  language not very precise I guess...
Former methods for grasp evaluation with shape uncertainty require sampling from  distributions on shape. The standard approach of drawing samples from a GPIS in 2D by means of a %%PA: a -> an
 evaluation on a uniform grid has a complexity of $O(n^6)$(2D) and $O(n^9)$ in the number of grid steps $n$.%%PA: grouping of words should try to make things easier to read/follow along; does 2D only apply to the O(n^6) or to the entire sentence?  aside from sentence structuring, it's hard to understand this previous sentence, what is the n^9 about? what is a grid step?  does it mean number of discretization levels for dimension?
%%PA: also, why ".." rather than "." to end the sentence?
We propose an alternative approximation%%PA: grouping of words is off; it's not an alternative approximation, it 's an alternative to sampling from shape distributions ..
 to sampling from shape distributions and demonstrate how that reduce complexity from $O(n^6)$ in 2D and $O(n^9)$ in 3D to $O(n^3)$ for evaluation of a single grasp. 
%%PA: how about including some intuition about what the alternative is / what main idea it is leveraging?
We furthermore introduce the idea of adaptive sampling in this context by formulating it as a multi-arm bandit problem for speeding up the selection of the highest quality grasp in a set of proposed grasps.  %%PA: --> cool!!
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

@@

%%PA: this citation type-setting is a bit funny to me, I am much more used to [12, 8, 10] or [12], [8], [10] rather than the current paper's typesetting as [12] [8] [10].  If you have seen it in a reputable place and it's the style you guys prefer then I am fine with it, of course
%%ZM: will fix as going through

\todo{Get High res GPIS visualizations, Incorporate next round of feedback}
Consider a robot packing boxes in a shipping warehouse environment. The robot will frequently encounter objects that it has not seen before. The robot will have to plan stable grasps without any prior information other than its sensor data. As seen in Fig. \ref{fig:noisy data}, with today's RGB and depth sensors, surface properties, such as specularity and transparency, can greatly effect the returned observations. Grasp planners based on deterministic algorithms are not designed to handle such noise and could fail. To plan grasps in a partially observed world, recent research has focused on incorporating uncertainity%%PA: --> spelling
 in the shape of the object \cite{kehoe2012estimating}, \cite{christopoulos2007handling}, \cite{zheng2005}. %%PA: why two dots? %%PA: and same paper is cited twice... %% ZM fixed

While past work has encoded uncertainty in a polygonal mesh representation \cite{kehoe2012estimating}, an alternative is to work with the signed distance fields (SDFs), a continuous valued function that is an implicit surface: zero-valued at the surface of the object, positive value outside the surface and negative valued inside the surface. This representation is growing in popularity in the robotics field for its ability to integrate range data in real time \cite{newcombe2011kinectfusion}\cite{curless1996volumetric}. To incorporate uncertainty one can use a Gaussian Process Implicit Surface (GPIS), a Gaussian process over signed distance field. Not only does GPIS present a straightforward and formal way to incorporate measurements from visual, laser and tactile sensors, they  also allow for a continuous differentiable function on shape, 
%%PA: continuous and differentiable (which I believe would be a redundant statement as differentiable implies continuous), or continuously differentiable?
which can be used for a feedback grasp controller, finding locally optimal grasps and active exploration  \cite{dragiev2011}, \cite{jeffs}, \cite{hollinger2013}.

\begin{figure}[ht!]
\centering
\includegraphics[width=8.5cm,height=4cm]{figures/Slide02.jpg}
\caption{Left: HD image of a common measuring cup from in a household environment. Right: Image taken from PR2's Primesense Carmine sensor, large parts of the measuring cup are not detected by the depth sensor and are not visible in the RGB image.}
\vspace*{-10pt}
\label{fig:noisy data}
\end{figure}

Given a method to represent shape uncertainty, a common technique to evaluate grasp quality is to sample from the distribution on shape and perform Monte-Carlo integration on a given grasp metric \cite{kehoe2012estimating}, \cite{kehoe2012toward}, \cite{christopoulos2007handling}. Applying this technique to GPIS requires an exhaustive sampling of the signed distance field, which scales $O(n^6)$ for a 2D $n \times n$ workspace and $O(n^9)$ for a 3D workspace.The computationally complexity of sampling is derived from the fact sampling from a Gaussian requires matrix inversion of the entire signed distance field. Our paper reduces this complexity to $O(n^3)$ by using the insight that for grasp quality evaluation one only cares about the parameters that define a grasp: contacts points, surface normals, center of mass and friction coefficient \cite{pokorny2013classical}. 
%%PA: that's neat!  let's have you include some of that in the abstract!
%%PA: also n^3 independent as to whether it's a 2-D or 3-D problem, or is n^3 specific to a particular dimensionality?
We constrain the contact points by considering the approach trajectory of a gripper.  Hence, sampling the whole signed distance field is not needed, but instead one can only work with the distributions on grasp parameters given the shape uncertainty model and gripper trajectory. In light of this our contributions are the following:

\begin{enumerate}
	\item Derivation of  distributions on grasp parameters given GPIS shape uncertainty model and approach trajectory of gripper.%%PA: grammar off
	\item  Demonstrating both theoretically and empirically how those distributions reduce the computational complexity of sampling.%%PA: -> computational %%ZM: fixed
	\item Applying adaptive sampling techniques to efficiently find high quality grasps in a given set of proposed grasps. 
\end{enumerate}

@@

 Past work on grasping under uncertainty has focused on state uncertainty \cite{goldberg1990bayesian}, \cite{goldberg1990stochastic}, \cite{stulp2011learning},  uncertainty in object pose \cite{christopoulos2007handling}, \cite{felip2009robust}, \cite{kim2012physically} or uncertainty in the location of contact with the object \cite{zheng2005}. Robust grasp selection for parallel jaw grippers on uncertain shapes was studied by Kehoe et al. for both zero-slip push grasps \cite{kehoe2012toward} and slip push grasps \cite{kehoe2012estimating} using Monte Carlo integration for the expected grasp quality, but this approach was limited to polygonal shapes.  Christopoulo et al. sampled spline fits for 2-dimensional planar objects to measure the quality of uncertainty, however it is has not been shown how a spline based method could incorporate non-visual sensing information for representing shape uncertainty.

 The choice of using Gaussian Process Implicit Surfaces to represent uncertainty, is based on the fact it provides a formal way to include various sources of noise from observations such as tactile, laser and visual. Futhermore, implicit surface representations are becoming increasingly popular in robotics due to their success in real-time surface modeling from range images \cite{curless1996volumetric}, \cite{newcombe2011kinectfusion}, \cite{hornung2013octomap}. Some exciting work done with GPIS representation are the following: Hollinger et al. used GPIS to perform active sensing on the hulls in underwater boats \cite{hollinger2013}. Dragiev et al. showed how GPIS can represent shapes for grasps and used  as a grasp controller on the continuous signed distance function \cite{dragiev2011}. Mahler et al. used GPIS representation to find locally optimal grasps by framing grasp planning as an optimization problem \cite{jeff}. %%PA: locally optimal anti-podal grasps?

  For grasp quality evaluation with shape uncertainty a common method involves sampling from the distribution on shape \cite{kehoe2012estimating}, \cite{kehoe2012toward}, \cite{christopoulos2007handling}. With GPIS this requires computationally intensive sampling from a signed distance field that is the dimension of the workspace. We propose an alternative distribution to sample from, based on the idea that we only need to consider the approach trajectory of the gripper.

Monte-Carlo integration involves drawing random samples from a distribution to approximate an integral \cite{caflisch1998monte}. While previous work has looked at quality evaluation of a single grasp with uncertainty \cite{christopoulos2007handling}, \cite{zheng2005}, few have compared many different grasps with uncertainty and efficiently chosen the best one.  Adaptive Sampling is the idea of allocating samples based on previous observations or rewards, which can be described as a multi-arm bandit problem \cite{barto1998reinforcement}. Prior work by Kehoe et al. \cite{kehoe2012toward} used an adaptive sampling approach that removed low quality grasps based on values received, but this method had no statistical guarantees and could lead to high quality grasps being removed. To achieve guarantees, we frame the problem as a "budgeted multi-arm bandit" problem, where exploration and exploitation are decoupled and the agent has to allocate resources to explore for a finite time then decide which arm to exploit  \cite{madani2004budgeted}. Drawing from the literature on Monte-Carlo sampling we estimate the confidence bounds of grasps and prune only those that are statistically distinguishable \cite{caflisch1998monte}.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width = 8.5cm, height = 14cm ]{figures/Slide03.jpg}
\caption{Six example objects illustrating transparency, specularity, sensor noise that illustrate the need for shape uncertainty: (from top to bottom) tape, squirt bottle, stapler, loofa, marker, water bottle. Displayed from right to left are the HD color image, a point cloud observation from a Primesense Carmine, GPIS visualization technique from \cite{jeffs}, the nominal shape on a $25 \times 25$ grid.  }
\vspace*{-10pt}
\label{fig:GPIS_TSDF}
\end{figure}
%\section{Related Work}

For our kernel choice we decided to use the square exponential kernel, a major reason for this was its differentiability. Other kernels relevant to GPIS are the thin-plate splines kernel and the Matern kernel \cite{williams2007}. %%PA: motivation seems a little weak; did you compare performance with other kernels? (must be other differentiable ones?) could something be added about why differentiability is important to our approach?

@@

The $L^1$ version of the metric works by taking as input the contact points $\textbf{c}_1,...,\textbf{c}_m$, surface normals $\textbf{n}_1,...,\textbf{n}_m$, center of mass $z$ and friction coefficient $\mu$. Then constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space. A wrench is defined as concatenation of a force and torque vector.  If the convex hull doesn't enclose the origin, the grasp is not in force-closure. Thus a grasp can be parameterized by the following tuple $g = \lbrace \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} \rbrace$, our method is applicable to all grasp metrics that represent a grasp as the tuple $g$, such as \cite{christopoulos2007handling}, \cite{li1988task}.

@@

\begin{align*}
E(Q(\Gamma)) \approx \sum_{i=1}^N Q(g|S_i,\Gamma) , S_i \in p(S) %%PA: 1/N missing?
\end{align*}

@@

Thus if the workspace is an $n \times n$ grid, the joint distribution is an  $n^2$ multi-variate Gaussian, due to $sd:\mathbb{R}^2 \rightarrow \mathbb{R}$.  Sampling from a Gaussian involves inverting the covariance matrix and inversion is in the naive way $O(n^3)$ \cite{petersen2008matrix}. %%PA: that last use of $n$ has a different meaning, that's confusing, use a different symbol than n, or just say in words it's cubic in the number of grid points
Thus the complexity of this operation is $O(n^6)$ in 2D and $O(n^9)$ in 3D.

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width = 17cm, height = 4.5cm]{figures/Slide04.jpg}
\caption{(Left to Right): Line of action for a given gripper on an uncertain surface representing a measuring cup. Distribution $p(c)$ as a function of $t$, the position along the line of action $\gamma(t)$. The two modes correspond to the different potential contact points, either the handle or the base of the cup. Lastly, the distribution on the surface normals (inward pointing) along $\gamma(t)$ described by equation \ref{eq:normal_dist}. }
\vspace*{-10pt}
\label{fig:GraspDist}
\end{figure*}

@@

%%PA: it's not clear to me where the savings are coming from; the goal was to avoid sampling from the GPIS; but now it seems the algorithm needs to sample from the GPIS after all to obtain the grasp parameters?  What am I missing here?  Please address not just in the paper, but also via email

%%PA: if you are indeed avoiding sampling from th GPIS now, then it'd be good to highlight that, and explain exactly how that was enabled...

%%PA: the entire Section V. is a bit confusing; reads very procedural, but not a very clean straightforwardly explained procedure, and the rationale / context / big idea is not explained...

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale = 0.3]{figures/Slide06.jpg}
\caption{Left: A surface with GPIS construction and expected center of mass (black X)
Right: The distribution on the density of each point assuming uniform density}
\vspace*{-10pt}
\label{fig:GPIS_MASS}
\end{figure}

@@

\section{Adaptive Sampling for Grasp Selection}
After determining how to efficiently compute the $E(Q(\Gamma))$, we need to now compute the full problem of Eq. \ref{eq:problem_def}, hence the selecting the best grasp plan $\Gamma^*$. While a standard approach to solving this problem would be to simply perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-arm bandit problem and forming a policy for selecting which grasp to sample. The motivation behind this is due to the expensive evaluation that our grasp metric Q can take \cite{ferrari1992} and the fact that the convergence of the expected quality of a typical grasp can take hundreds of evaluations as shown in Fig. \ref{fig:sampling_convergence}.  %%PA:-> grammar?

\begin{figure}[ht!]
\centering
\includegraphics[width=8.5cm,height=9cm]{figures/Slide11.jpg}
\caption{Convergence of expected grasp quality, $E(Q(g))$,  for a typical grasp. You can see it can take hundreds of evaluations to correctly estimate the expected grasp quality, thus it is important to  intelligently allocate sampling resources}
\vspace*{-10pt}
\label{fig:sampling_convergence}
\end{figure}

@@

More formally an agent is given a set prior distributions $\mathcal{P}(1,...,K)$ for the K arms based on the awards seen.%%PA: -> rewards?  
 At each interval an arm $I_t$ is pulled based on some allocation strategy $\psi_t \in \lbrace 1,...,K \rbrace$. This happens until a stopping signal is given at which point an arm (or grasp plan) is chosen based on a recommendation strategy $\zeta_t \in \lbrace 1,...,K \rbrace$.

@@

%%PA: hard to follow along, lots of notation, is it really necessary to introduce that many new symbols to get the point across?

@@

%%PA: how does a single number define an interval?

%%PA: again lots of notation and symbols, how about explaining it primarily in plain words, would anything be lost? if so, introduce symbols / equations for what you lose as necessary...

%%PA: to me this doesn't sound like uniform allocation; while I can't actually follow along, my hunch is that you have confidence intervals, and at each step you consider which grasps are still in contention for being a winner based on their confidence intervals, and then sample a shape (is is a shape? is it something else that you sample?) once for each grasp

@@

%%PA: it'd be nice to have the text be such that you can read it, and from that understand what the conclusions are from the experimentation...

\begin{figure}[ht!]
\centering
\includegraphics[width=8.5cm,height=9cm]{figures/Slide12.jpg}
\caption{Time it took to sample from 100 grasp distributions for a given resulution of the workspace. Blue line is sampling from $p(sd(\mathcal{R}))$ or shapes and Green is sampling from $p(g)$ or the calculated distribution on grasps. As you can see sampling from the calculated distributions scales much better. }
\vspace*{-10pt}
\label{fig:speed_dif}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=8.5cm,height=9cm]{figures/Slide09.jpg}
\caption{Comparison of two sampling methods. Green is the adaptive bandit method that actively chooses which one to sample and Blue is the naive Monte-Carlo method. We measure their ability to converge in terms of simple regret Eq. \ref{eq:simple_regret} averaged over 100 runs. We had them determine the best grasp when $|G|=1000$. As you can see our method converges much faster with an average of evaluation of 4 samples per grasp. We start the process though by deterministically evaluating every grasp 2 times to achieve a baseline, which explains the first part of the graph.}
\vspace*{-10pt}
\label{fig:simple_regret}
\end{figure}

%%PA: was this an experiment on one shape distribution? that'd be rather anecdotal then... Did you run more extensive experiments?
